Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-17 paper.qmd
Updated 10X Genometic bib

```{r}
#| label: best-fit-tsne
#| fig-cap: "Lifting the \\gD{} fitted model into \\pD{}. Two projections of the \\pD{} fitted model overlaying the data are shown in b, c. The fit is reasonbly tight with the data in one cluster (top one in b), but slightly less so in the other cluster probably because it is in $3-\\text{D}$. Notice also that, in the \\gD{} layout the two clusters have internal gaps which creates a model with some holes. This lacy pattern happens regardless of the hyper-parameter choice, but this doen't severely impact the \\pD{} model representation."
#| fig-width: 8
#| fig-height: 2

>>>>

```{r}
#| label: best-fit-tsne
#| fig-cap: "Lifting the \\gD{} fitted model into \\pD{}. Two projections of the \\pD{} fitted model overlaying the data are shown in b, c. The fit is reasonbly tight with the data in one cluster (top one in b), but slightly less so in the other cluster probably because it is in $3\\text{-}D$. Notice also that, in the \\gD{} layout the two clusters have internal gaps which creates a model with some holes. This lacy pattern happens regardless of the hyper-parameter choice, but this doen't severely impact the \\pD{} model representation."
#| fig-width: 8
#| fig-height: 2
